Applicaton

### 2023-12-31 app_par.qmd
app50
tabsets

```{r, echo=F}
# Start on 50
md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
mda <- md[[paste0("app",params$name)]]
apprda <- get(load(paste0(rprojroot::find_rstudio_root_file(),'/data/app',params$name,".rda")))
app_a_out <- seloutput(selreport(apprda,mda))
```

@@

[Link to raw data and independent calculcations](`r mda$sht$url`)
[@sol2022_1]

::: {.panel-tabset}
### `r mda$tabsets[[1]]`
```{r, echo=F}
kableExtra::kbl(app_a_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
```
### `r mda$tabsets[[2]]`
```{r, echo=F, out.width="60%"}
app_a_out[['corxy']]
```
### `r mda$tabsets[[3]]`
```{r, echo=F, out.width="60%"}
app_a_out[['qunt']]
```
### `r mda$tabsets[[4]]`
```{r, echo=F}
app_a_out[['ro3d']]
```
### `r mda$tabsets[[5]]`
```{r, echo=F, out.width="60%"}
app_a_out[['regr']]
```
### `r mda$tabsets[[6]]`
```{r, echo=F, out.width="60%"}
app_a_out[['resp']]
```
:::

@@

### References

::: {#refs}
:::

>>>>

```{r, echo=F}
md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
mda <- md[[paste0("app",params$name)]]
apprda <- get(load(paste0(rprojroot::find_rstudio_root_file(),'/data/app',params$name,".rda")))
app_a_out <- seloutput(selreport(apprda,mda))
```

```{r, echo=F}
apn <- paste0('app','1')
mda <- md[[apn]]
```

@@

[Link to raw data and independent calculcations](`r mda$sht$url`)

---

::: {.panel-tabset}

### `r mda$tabsets[[1]]`
```{r, echo=F}
kableExtra::kbl(app_a_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
```
### `r mda$tabsets[[2]]`
```{r, echo=F, out.width="60%"}
app_a_out[['corxy']]
```
### `r mda$tabsets[[3]]`
```{r, echo=F, out.width="60%"}
app_a_out[['qunt']]
```
### `r mda$tabsets[[4]]`
```{r, echo=F}
app_a_out[['ro3d']]
```
### `r mda$tabsets[[5]]`
```{r, echo=F, out.width="60%"}
app_a_out[['regr']]
```
### `r mda$tabsets[[6]]`
```{r, echo=F, out.width="60%"}
app_a_out[['resp']]
```
:::

@@
